Enforced Invariant Confluence

### 2018-02-20 doc/paper_redux/new_statebased_sufficient.tex
WIP

\section{\dIconfluence{} and \dIreduction{}}
A \defword{join-free} expression $e = t_1(t_2(\ldots t_n(s_0) \ldots))$ is an
expression that does not contain a join.

We say $T$ is \defword{\dIconfluent{}} if for every pair $e_1$ and $e_2$ of
join-free expressions, $\Irec{e_1}$ and $\Irec{e_2}$ implies that $I(e_1 \join
e_2)$. Intuitively, \dIconfluence{} is the same thing as \Iconfluence{} with
the added restriction that subexpressions are join-free.

We say $T$ is \defword{\dIreducible{}} if for every pair $e_1$ and $e_2$ of
join-free expressions, $\Irec{e_1 \join e_2}$ implies that there exists some
join-free expression $e_3$ such that $\Irec{e_3}$ and $eval(e3) = eval(e1 \join
e_2)$.  Intuitively, \dIreduction{} allows us to eliminate join operators by
substituting $e_1 \join e_2$ (which contains 1 join) with $e_3$ (which does not
contain any joins).

@@

>>>>

\section{New Sufficient State-Based Conditions}
In this section, we outline a new sufficient condition for state-based
\Iconfluence{} that is more general than the one in
\clmref{statebasedsufficient}. To prove that the condition is sufficient, we
introduce the concepts of \dIconfluence{} and \dIreduction{}.

\begin{definition}
  A \defword{join-free} expression $e = t_1(t_2(\ldots t_n(s_0) \ldots))$ is an
  expression that does not contain a join.
\end{definition}

\begin{definition}
  $T$ is \defword{\dIconfluent{}} if for every pair $e_1$ and $e_2$ of
  join-free expressions, $\Irec{e_1}$ and $\Irec{e_2}$ implies that $I(e_1
  \join e_2)$.
\end{definition}

Intuitively, \dIconfluence{} is the same thing as \Iconfluence{} with
the added restriction that subexpressions are join-free.

\begin{definition}
  $T$ is \defword{\dIreducible{}} if for every pair $e_1$ and $e_2$ of
  join-free expressions, $\Irec{e_1 \join e_2}$ implies that there exists some
  join-free expression $e_3$ such that $\Irec{e_3}$ and $eval(e3) = eval(e1
  \join e_2)$.
\end{definition}

Intuitively, \dIreduction{} allows us to eliminate join operators by
substituting $e_1 \join e_2$ (which contains 1 join) with $e_3$ (which does not
contain any joins).

@@

\begin{claim}
  Consider a state-based object $(S, s_0, \join)$, a set of transactions $T$,
  and an invariant $I$. $T$ is \Iconfluent{} if the following criteria are met:
  \begin{enumerate}
    \item
      $(S, \join)$ is a semilattice.
    \item
      For every $t \in T$, there exists some $t': S \to S$ such that for all
      $s \in S$, $t(s) = s \join t'(s)$.

    \item
      For every pair of transactions $t_1, t_2 \in T$ and for all states $s \in
      S$, $t_1(t_2(s)) = t_2(t_1(s))$.

    \item
      For every pair of transactions $t_1, t_2 \in T$ and for all states $s \in
      S$, if $I(s)$, $I(t_1(s))$, and $I(t_2(s))$, then $I(t_1(s) \join
      t_2(s))$.
  \end{enumerate}
\end{claim}
\begin{proof}
  foo
\end{proof}

\todo{State conditions}
\todo{Prove sufficient}
\todo{Show more general than naive conditions}

### 2018-02-20 doc/paper_redux/sufficient_conditions.tex
WIP

The conditions in \clmref{statebasedsufficient} and \clmref{opbasedsufficient}
are not necessary. Intuitively, this makes quite a bit of sense. Neither
condition depended on the initial state $s_0$, and both
\clmref{statebasednotnecessary} and \clmref{opbasednotnecessary} exploit this.
If we relax our assumption of a fixed start state, then both these conditions
become sufficient and necessary.

\todo{Prove this more carefully. It's pretty straightforward though.}

>>>>

The conditions in \clmref{statebasedsufficient} and \clmref{opbasedsufficient}
are not necessary. Intuitively, this makes quite a bit of sense. The condition
in \clmref{statebasedsufficient} doesn't depend on $T$ and neither condition
depends on the initial state $s_0$. However, if we relax our assumption of a
fixed start state $s_0$ and instead allow replicas to begin with an arbitrary
state, then both conditions are sufficient and necessary. Alternatively, if
every state in $S$ is reachable from $s_0$, then the conditions are sufficient
and necessary.

\todo{Prove these facts more carefully. It's pretty straightforward though.}

% | Data Model                              | I           | SC  | T | IC  |
% | State based set with union              | phi(x)      | yes |   | yes |
% | State based two sets with union         | foreign key | yes |   | yes |
% | State-based increment-decrement counter | >           |
